Changes in Patterns of Geometric Sign Groupings as a Model of Social Dynamics Across Aurignacian Phases

### 2025-04-29 Extra/undergraduate-research-symposium-images.qmd
stash

seriation_proto <- 
  produce_clusters(proto_artifact_data, 
                   proto_unique_data, 
                   # BM: not sure why this one gets the 
                   # colour differently from the others
                   color_palette = c("#FFFFB3", "#8DD3C7"),
                   method = "seriation")

@@

seriation_evolved <- 
  produce_clusters(evolved_artifact_data, 
                   evolved_unique_data, 
                   method = "seriation")

x <- plot_grid(seriation_trans,
          seriation_proto, 
          seriation_early , 
          seriation_evolved, 
          ncol = 2, 
          align = "hv", 
          labels = c("Transitional", "Proto", "Early", "Evolved"), label_size = 5, 
          scale = c(1.07, 1.07, 1.07, 1.07))

ggsave(x, 
      filename =  "seriation.png",
       h = 2.3, w = 3.7,
       bg = "white")

@@

```{r}
network_trans <- trans_network(trans_artifact_data)
network_proto <- produce_clusters(proto_artifact_data, proto_unique_data, method = "network")
network_early <- produce_clusters(early_artifact_data, early_unique_data, method = "network")
network_evolved <- produce_clusters(evolved_artifact_data, evolved_unique_data, method = "network")

y <- plot_grid(network_trans, network_proto, network_early, network_evolved, 
          ncol = 2, align = "hv", labels = c("Transitional", "Proto", "Early", "Evolved"), label_size = 5)

ggsave(y, 
      filename =  "network.png",
       h = 8, w = 10,
       bg = "white")
```

>>>>

seriation_proto <- produce_clusters(proto_artifact_data,  
                                    proto_unique_data, 
                                    color_palette = c("#FFFFB3", "#8DD3C7"),
                                    method ="seriation")

@@

seriation_evolved <- produce_clusters(evolved_artifact_data, 
                                      evolved_unique_data, 
                                      method = "seriation")
```

```{r}
network_trans <- produce_clusters(trans_artifact_data, trans_unique_data, method = "network")
network_proto <- produce_clusters(proto_artifact_data, proto_unique_data, method = "network")
network_early <- produce_clusters(early_artifact_data, early_unique_data, method = "network")
network_evolved <- produce_clusters(evolved_artifact_data, evolved_unique_data, method = "network")

@@

```{r}
ser_net_trans <- plot_grid(seriation_trans, network_trans, align = "hv", labels = "AUTO", rel_widths = c(1.3, 1.4))
ser_net_proto <- plot_grid(seriation_proto, network_proto, align = "hv", rel_widths = c(1.4, 1.4))
ser_net_early <- plot_grid(seriation_early, network_early, align = "hv", rel_widths = c(1.65, 1.8))
ser_net_evo <- plot_grid(seriation_evolved, network_evolved, align = "hv", rel_widths = c(1.4, 1.4))

final <- plot_grid(ser_net_trans, ser_net_proto, ser_net_early, ser_net_evo, align = "hv", ncol = 1, labels = c("Transitional", "Proto", "Early", "Evolved"))

ggsave(final, 
      filename =  "poster.png",
       bg = "white", h = 9, w = 4.5)
```

```{r}
ser_net_trans <- plot_grid(seriation_trans, network_trans, align = "hv", labels = "AUTO", ncol = 1)
ser_net_proto <- plot_grid(seriation_proto, network_proto, align = "hv", ncol = 1)
ser_net_early <- plot_grid(seriation_early, network_early, align = "hv", ncol = 1)
ser_net_evo <- plot_grid(seriation_evolved, network_evolved, align = "hv", ncol = 1)

final <- plot_grid(ser_net_trans, ser_net_proto, ser_net_early, ser_net_evo, align = "hv", ncol = 4, labels = c("Transitional", "Proto", "Early", "Evolved"))

ggsave(final, 
      filename =  "poster2.png",
       bg = "white", w = 12)

```{r}
ser_plot <- plot_grid(seriation_trans, seriation_proto, seriation_early, seriation_early, align = "hv", ncol = 1, labels = c("Transitional", "Proto", "Early", "Evolved"), label_size = 9)
net_plot <- plot_grid(network_trans, network_proto, network_early, network_evolved, align = "hv", ncol = 1)

  final <- plot_grid(ser_plot, net_plot, align = "hv", ncol = 2, rel_widths = c(1.3, 1), labels = "AUTO", label_x = c(0, -0.07))

ggsave(final, 
      filename =  "poster3.png", bg = "white", w = 5, h = 7)
```
